\section{Meta groups}
During this sprint the meta groups have been used in different ways.
In the following the different groups activities will be elaborated and evaluated.

\subsection{Frontend}
Throughout this sprint the frontend meta group saw very little action, since by this point of the project most frontend coordination related issues had been sorted out.
Hence the group has fulfilled its purpose for this project and will no longer act as an active group, but could be re-activated at a later point if needed.

\subsection{Backend}
As described in \autoref{CollabAPIUpdate} there was an update to the API, made by collaborative work across project groups.
This update made all of the tests fail due to the change in the way images were stored.
So, during sprint three the backend meta group was assembled for an API workshop where the primary goal of the day was to make the unit tests work again.
During the workshop all groups sent their backend representatives in order to work on the problems.
At the end of the workshop all test were working again and the API had been cleaned up in regards to the endpoints.

\subsection{Server}
During the last sprints a lot of server work had been completed but some of the group members felt that they had lost overview of the changes.
In order to bring everybody up to date, a server meta group meeting were setup where our group presented the work we had done and elaborated on the decisions made along the way.

After the meeting, each group felt sufficiently informed to complete the rest of the project period and no other meeting was scheduled.
