\section{Review}
As a part of Scrum of Scrums we held a review meeting, where we discussed what progress had been made that was relevant to the product.
Most groups did not make any significant progress.
This was mostly due to the issues encountered with Xamarin.
There were no user stories that had been completed fully yet, and those that were had not been reviewed yet, so our greatest progress was that we had discovered some flaws and missing functionality in the core that had been written over the weekend.

One flaw was when logging out the app, it would crash; once it reached the login screen a second time, as the login screen had problems with the id of the screen that has been loaded multiple times. 
This was an issue with the core that had been written over the weekend, as the issue was not urgent and it was decided that the issue would be solved at a later time.

In addition to the login screen issue, a couple of groups had an issue where they did not know what the proper way to send and recieve data from screen to screen was.
The usual way would be to use the constructor, but this was not possible yet. 
It was possible to write the code that was suspposed to send/receive. 
However, it would not be able to communicate yet, so it would not work as intented until the necessary functionality was added to the core.
This was suggested to be solved, at a later time, by the same group that wrote the flutter core, as they were familiar with how the core was structured and the group with the most experience in flutter.
