\section{Planning}
The sprint planning was held on the 25\textsuperscript{th} of February, and was done by having a meeting with the entire Giraf organization present. 
The product owner group presented some user stories as well as what the goal of the project was. 
The customers wanted more stability and reliability in the apps that already works, and did not care whether new and exciting functionality was added. 

After the presentation, each group picked 3 user stories that they wanted to complete, even though the user stories was not necessarily a high priority for the project. 
The idea was that the groups got something they wanted to work with as a startup and would then later pick based on priority.

Each group was assigned 1 of their top 3 user stories, and the user story was then estimated on how long it would take to complete.
If the group were able to complete the user story early in the sprint, they could ask the PO group for additional user stories.
Hence the PO group could make sure that all user stories assigned in the sprint were completed during the sprint.

We were not certain of the time it would take to complete the user story that we had picked, especially as another group had a user story that potentially would conflict with some parts of our user story, hence this conflict had to be resolved.
 
Our user story was: "As a guardian I would like to confirm with a password that the system is changing to guardian mode so that a citizen cannot gain access to it".

The other group had the user story: "As a guardian, I would like that the app is fully available offline so that I can still use it if the internet is down"

So as our user story was regarding authentication of a guardian entering guardian mode and the other group's were to make the entire app work offline, including login authentication, an agreement to who would work on what had to be found, such that we did not get any duplicate work.
As our issue contained some frontend while the others only concerned the backend we agreed that they would resolve the backend work and we would work on the frontend part of our user story and then use the new login functionality that they made.