\chapter*{Preface}
This report is written during the 6\textsuperscript{th} semester of the bachelor's degree in Software at Aalborg University.
It is written for the study board of computer science at the School of Information and Communication Technology.
The report is written with the guidance our supervisors Tiantian Liu(\href{http://personprofil.aau.dk/profil/145323}{AAU profile}) and Ulrik Nyman(\href{http://personprofil.aau.dk/profil/110550}{AAU profile}).

The topic of the semester is 'Developing Complex Software Systems'.

The purpose of this project is to gain experience with development of a larger and more complex software system than the earlier semesters could justify.
The project is structured as a multi group project where multiple groups are developing on the same codebase and with the same costumers.

All groups work as full stack teams to ensure that the quality of the product is as high as possible and to ensure a high throughput on user stories.

The software repository, where the code is available, can be found on \href{https://github.com/aau-giraf/}{GitHub} and the released version can be found on the \href{https://play.google.com/store/apps/details?id=dk.aau.cs.giraf.weekplanner}{Google PlayStore}.
It was originaly planned to have the released version available on the Apple App Store as well, but throughout the entire semester we were unable to uptain a licence for releasing.
However, late in the project period a volunteer organization was established in order to obtain an Apple Developer License and the app will thus be uploaded to the Apple AppStore after the project hand in.

This report contains sections in \autoref{CAP:Intercollaboration} that are written in collaboration with other groups and these sections will thus be identical with sections in their reports.

Throughout this report hyperlinks has been used to reference to external sources, hence this report is meant for digital consumption and should not be printed. 

- \textit{Group SW612F19}

\newpage
