\section{Documentation Overview}\label{SEC:DocumentationOverview}
During the hand over of the project from the last semester, we got access to the Phabricator and GitLab system. 
Phabricator is project management system that enables developer teams to share both code and documentation. 
Phabricator also has some build in code review functions and allows for communication via chats. 

The earlier semester however had chosen to host the Phabricator server along side the production API's and database.

The old semester also had chosen to use GitLab on a selfhosted server, again also along side the production services. 
This meant that the added responsibility on the servers made the entire project unsafe and it has hence quickly decided that the GitLab and Phabricator should be migrated onto GitHub. 

This migration means that all documentation is now centralized on the GitHub repository \href{https://github.com/aau-giraf/wiki}{Wiki}. 
By hosting it on GitHub the repository can be transformed into an webpage more suitable for public consumption.
The GitHub webpage can be seen on this \href{https://aau-giraf.github.io/wiki/}{link}.

Once all relevant information was migrated from Phabricator to GitHub, the Phabricator server was shut down. 
Before the server was removed/deleted by ITS, a backup of both the web server and database was created and stored elsewhere.

By migrating both the GitLab and Phabricator to GitHub the amount of responsibilities of the system was reduced. 
This meant that the focus of the project could be aimed at the actual development of the product and not on the tools needed.
