\section{Planning}
For this sprint the planning was held in a more relaxed fashion.
It was not so much planning as it was an introduction to what the general goal of the sprint was.
The reasoning is that we believed, from the feedback of sprint 1's retrospective, that we would achieve a faster and easier workflow by using the issue system from GitHub to see what current user stories were available and a priority for the sprint. 

This switch in workflow also means that we are no longer using scrum of scrums, at least not in a traditional sense, but we are using a lot of the elements that it provides.
The only "real" change is the way that we "plan" a sprint; now we use GitHub issues for user stories, so each issue on GitHub is equivalent to a user story and we also do not assign groups to user stories at the planning meeting. 
Instead we will be assigning ourselves to a fitting amount of user stories, that we choose in collaboration with the PO group, at any time during the sprint, so if we run out of user stories we pick a new one from GitHub. 

\subsection{Goals}
The goal of this sprint was to make the flutter rewrite of the app more user friendly and improve the GUI in comparison to the, now, old xamarin implementation.
In order to make the app more user friendly we were to implement more basic functionality into the flutter version of the app, as it was very lacking at this point.
Most of the basic functionality was already described as user stories and available on GitHub. 
These user stories were mainly related to making a flutter version of the old xamarin features and in the process improve and update them in accordance with the goals.
To improve the GUI of the app we were to either use the prototypes that they had already attached to the user story or follow the design guide that the PO group made.

\subsection{Our initial user stories}
After the introduction to the sprint, the PO group went out to each group to get some perspective of how far along everyone were with their current user stories, that remained from sprint 1, and to check whether or not a group was free to take new user stories.

We were essentially done with our user story, as we were depending on another group's changes to the app to be merged with our changes.
So with us being essentially done, we picked some high priority user stories in collaboration with the PO group.
These user stories were:

\begin{enumerate}
\item "As a guardian I would like to be prompted for a password when changing from citizen to guardian mode, so that a citizen cannot access the guardian mode"
\item "As a guardian I would like to be able to switch from citizen mode to guardian mode with the press of a button so that I can change the users schedule without restarting the application"
\end{enumerate}

The first user story depends on the second user story, so that when the app is in citizen mode a guardian can with their credentials log in as a guardian, which is in essence an administrator, by using the button that the second user story is about. 
%Maybe write more in depth about the user stories?
