\chapter{Template for Code Review Checklist} \label{app:code-review-checklist}
\textbf{TEAMTAG} you have been assigned this. Here's your checklist. I
marked \textbf{PERSONTAG} as the reviewer, but you might change it as you
like. Please use the following checklist. Feel free to check it off as
you go along.

\section{Code Design}
\begin{itemize}
\item Is the code in the right place? (Both in terms of folder
 structure and class structure)
\item Could this code, to the best of your knowledge, have reused
 existing code?
\item Is the code over-engineered? Examples of over-engineering:
 Implemented behavior for future problems
\item Does it introduce functionality that is not necessary for
 solving the problem?
\end{itemize}

\section{Code Readability and Maintainability}
\begin{itemize}
\item Are names meaningful and self-documenting?
\item Is it understandable, by reading the code, what it does?
\item Is the code simple and readable? i.e. it contains no "hack",
 or obscure solution.
\item Is it understandable, by reading the tests, what they do?
\item Do the tests cover sensible cases? Both happy paths and
 exception paths?
\item Do the tests cover the full functionality? i.e., will the
 tests fail if some of the requested functionality is missing?
\item Are error messages in the code understandable?
\item Are confusing sections of code covered by comments?
\end{itemize}

\section{Functionality}
For this part, open the app, and test:

\begin{itemize}
\item Are the features that the code claims to implement, actually
 implemented?
\item Does it look like the code has bugs?
\item Are all new screens reachable through in-app navigation?
\end{itemize}

\section{Points for Discussion and Reflection}
\begin{itemize}
\item Are UI messages, that the user might meet, actually helpful?
\item Are there errors that are bad practice? Like, hard-coding a
 test database connection?
\item Is there well written code in this? Remember to tell the
 developer!
\end{itemize}
